
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-1pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingUpdated}[5]{
\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & {\small #4} \\
      \textit{\small#5}
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\huge Sahil Yogesh Hadke} \\ \vspace{1pt}
    \small +1-6026936593 $|$ \href{mailto:shadke1@asu.edu}{\underline{shadke1@asu.edu}} $|$ 
    \href{https://sahil.hadke.in/}{\underline{https://sahil.hadke.in/}} $|$
    Tempe, AZ
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
  
  
  
  \resumeSubheadingUpdated
  {Arizona State University}{December 2025}
    {Masters Science - Computer Science}{4.3/4}
    {Relevant Courses:{Semantic Web Mining, Data Visualization, Knowledge Representation Reasoning}
    }
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Programming Languages}{: Python, Java, C++, JavaScript} \\ \textbf{Frameworks/Tools}{: Node, Express, React, Web Scraping, Selenium, Unity 3D, AWS} \\  
    }}
 \end{itemize}

  %-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

       
    \resumeSubheading
      {Software Engineer}{May 2022 -- December 2023}
      {FIS}{Pune, India}
      \resumeItemListStart
      
        \resumeItem{Saved 1500 hours developing and implementing an automated funding booking system using Selenium Java.}
        
        \resumeItem{Contributed 750 hours/year savings automating web-based project management processes}
        
        \resumeItem{Worked in an Agile environment, following Agile principles and practices in project execution.}
        
      \resumeItemListEnd
       
    \resumeSubheading
      {Full Stack Developer - Internship}{December 2020 -- June 2022}
      {OG Advertising Private Limited}{Pune, India}
      \resumeItemListStart
      
        \resumeItem{Led an 80\% reduction in manual efforts by developing a web application that automated invoice generation.}
        
        \resumeItem{Collaborated with prestigious educational institutes in India, delivering custom website solutions that met unique demands.}
        
        \resumeItem{Worked on AWS EC2 Instances, utilizing Web Host Manager and cPanel for website hosting}
        
      \resumeItemListEnd
       
    \resumeSubheading
      {Studio Associate - Part Time}{April 2024 -- Present}
      {Next Lab, ASU}{Tempe, AZ}
      \resumeItemListStart
      
        \resumeItem{Collaborating closely with Unity 3D and C\# developers to integrate system functionalities seamlessly into game development projects}
        
        \resumeItem{Worked on AWS EC2 Instances, utilizing Web Host Manager and cPanel for website hosting}
        
        \resumeItem{Ensuring optimal performance and compatibility with project requirements}
        
      \resumeItemListEnd
    
    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
       
    \resumeProjectHeading
    {\textbf{JobTailor - Personalized Resume and Cover Letter Solution} \\ \emph{Python, LLM APIs, Web Scraping, Text Mining}}{}
      \resumeItemListStart
      
        \resumeItem{Developed an automated system using Python, LLM APIs, web scraping, and text mining to streamline the customization of resumes and cover letters.}
        
        \resumeItem{Implemented a feature that analyzes job descriptions using text mining techniques to provide metrics on similarity and tailors the resume to job requirements.}
        
        \resumeItem{Ensured the project's end-to-end functionality, including web scraping job listings, parsing input documents, and generating final tailored resumes and cover letters in PDF format.}
        
      \resumeItemListEnd
       
    \resumeProjectHeading
    {\textbf{RAG Application} \\ \emph{Python, LLM APIs, Web Scraping, Text Mining}}{}
      \resumeItemListStart
      
        \resumeItem{Developed a Retrieval-Augmented Generation (RAG) application:}
        
        \resumeItem{Leveraged LangChain to create a web-based RAG model, enhancing text generation with relevant retrieved content.}
        
        \resumeItem{Implemented a recursive web crawler to gather and preprocess data from multiple web pages for comprehensive data coverage.}
        
      \resumeItemListEnd
       
    \resumeProjectHeading
    {\textbf{Customer Relationship Management Tool} \\ \emph{CodeIgniter, PHP, MySQL, Bootstrap}}{}
      \resumeItemListStart
      
        \resumeItem{Developed a custom CRM tool using CodeIgniter, PHP, MySQL, and Bootstrap, which was utilized by multiple educational institutes in Pune to manage leads and admission campaigns, resulting in a 70\% reduction in manual efforts.}
        
        \resumeItem{Implemented lead aggregation from various sources, including websites, Facebook, and Google, into a centralized dashboard accessible to faculty members for efficient lead management.}
        
        \resumeItem{Enhanced administrative oversight by providing insights into lead closure rates per faculty, improving strategic decision-making and campaign effectiveness.}
        
      \resumeItemListEnd
    
   

    \resumeSubHeadingListEnd



%


%-------------------------------------------
\end{document}

